Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-07 manuscript/supplementary_information.Rmd
acknowledging meta-analysis was not pre-registered
Update supplementary_information.Rmd

Comparisons between values were partly automated through the use of a custom R function (https://osf.io/teuzb/) that accounted for rounding errors by rounding new values to the same number of decimal places as old values prior to computing the percentage error and classifying the value as a match, minor discrepancy, or major discrepancy. Note that for `r data_values %>% filter(!is.na(eyeballCheck)) %>% nrow()` values reported relative to a threshold (e.g., p < 0.05) or embedded in figures, we could not directly calculate percentage error and it was necessary to ‘eyeball’ (i.e., visually compare side-by-side) the values to confirm a match.

@@

@@

Code Ocean reproducible analysis container: https://doi.org/10.24433/CO.8022934.v1

>>>>

Comparisons between values were partly automated through the use of a custom R function (https://osf.io/teuzb/) that accounted for rounding errors by rounding reanalysis values to the same number of decimal places as original values prior to computing the percentage error and classifying the value as a match, minor discrepancy, or major discrepancy. Note that for `r data_values %>% filter(!is.na(eyeballCheck)) %>% nrow()` values reported relative to a threshold (e.g., p < 0.05) or embedded in figures, we could not directly calculate percentage error and it was necessary to ‘eyeball’ (i.e., visually compare side-by-side) the values to confirm a match.

@@

The pre-registered protocol does not state that we will run a meta-analysis. When writing up the present study, we decided it would be useful to run a meta-analysis to synthesize the evidence with the study by Hardwicke et al. (2018) which is highly comparable in goal and design.

@@

Code Ocean reproducible analysis container: https://doi.org/10.24433/CO.8022934.v2
